3.9: Logarithmic Models - R Practice

### 2019-11-21 static/r/21-r-practice-rmd.Rmd
Add class 21 content

---
title: "3.9: Logarithmic Regression - R Practice"
editor_options: 
  chunk_output_type: console
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(pander)
source(file.path(here::here(), "lib", "graphics.R"))
```

@@

### Part A
Create a new variable for $Age^2$. Then run a quadratic regression.

### Part B
Try running the same regression using the alternate notation: `lm(Y~X+I(X^2))`. This method allows you to not have to create a new variable first. Do you get the same results?

### Part C
Write out the estimated regression equation.

### Part D
Is this model an improvement from the linear model?^[Check $R^2$.]

### Part E
Write an equation for the marginal effect of `Age` on `Amount`.

### Part F
Predict the marginal effect on `Amount` of being one year older when you are 18.  How about when you are 40?

### Part G
Our quadratic function is a $U$-shape. According to the model, at what age is the amount of the fine minimized?

### Part H
Create a scatterplot between `Amount` and `Age` and add a a layer of a linear regression (as always), and an additional layer of your predicted quadratic regression curve. The regression curve, just like any regression *line*, is a `geom_smooth()` layer on top of the `geom_point()` layer. We will need to customize `geom_smooth()` to `geom_smooth(method="lm", formula="y~x+I(x^2)` (copy/paste this verbatim)! This is the same as a regression line (`method="lm"`), but we are modifying the formula to a polynomial of degree 2 (quadratic): $y=a+bx+cx^2$.

@@

# Question 4

@@

# Question 5

@@

# Question 6

@@

## Part A
Creating new variables as necessary, run a **linear-log** model of `Amount` on `MPHover`. Write down the estimated regression equation, and interpret the coefficient on `MPHover` $(\hat{\beta_1})$. Make a scatterplot with the regression line.^[Hint: The simple `geom_smooth(method="lm")` is sufficient, so long as you use the right variables on the plot!]

## Part B
Creating new variables as necessary, run a **log-linear** model of `Amount` on `MPHover`. Write down the estimated regression equation, and interpret the coefficient on `MPHover` $(\hat{\beta_1})$. Make a scatterplot with the regression line.^[Hint: The simple `geom_smooth(method="lm")` is sufficient, so long as you use the right variables on the plot!]

## Part C
Creating new variables as necessary, run a **log-log** model of `Amount` on `MPHover`. Write down the estimated regression equation, and interpret the coefficient on `MPHover` $(\hat{\beta_1})$. Make a scatterplot with the regression line.^[Hint: The simple `geom_smooth(method="lm")` is sufficient, so long as you use the right variables on the plot!]

## Part D
Which of the three log models has the best fit?^[Hint: Check $R^2$]

# Question 7
Return to the quadratic model. Run a quadratic regression of `Amount` on `Age`, `Age`$^2$, `MPHover`, and all of the race dummy variables. Test the null hypothesis: *"the race of the driver has no effect on Amount"*

# Question 8

>>>>

---
title: "3.9: Logarithmic Models - R Practice"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    #theme: 
    toc: true 
    toc_depth: 3
    toc_float: true
    code_folding: show
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

Create a new variable for $Age^2$. Then run a quadratic regression.

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

Try running the same regression using the alternate notation: `lm(Y~X+I(X^2))`. This method allows you to not have to create a new variable first. Do you get the same results?

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part C

Write out the estimated regression equation.

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part D

Is this model an improvement from the linear model?^[Check $R^2$.]

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part E

Write an equation for the marginal effect of `Age` on `Amount`.

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part F

Predict the marginal effect on `Amount` of being one year older when you are 18.  How about when you are 40?

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part G

Our quadratic function is a $U$-shape. According to the model, at what age is the amount of the fine minimized?

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part H

Create a scatterplot between `Amount` and `Age` and add a a layer of a linear regression (as always), and an additional layer of your predicted quadratic regression curve. The regression curve, just like any regression *line*, is a `geom_smooth()` layer on top of the `geom_point()` layer. We will need to customize `geom_smooth()` to `geom_smooth(method="lm", formula="y~x+I(x^2)` (copy/paste this verbatim)! This is the same as a regression line (`method="lm"`), but we are modifying the formula to a polynomial of degree 2 (quadratic): $y=a+bx+cx^2$.

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

@@

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

## Question 4

@@

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

## Question 5

@@

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

## Question 6

@@

### Part A
Creating new variables as necessary, run a **linear-log** model of `Amount` on `MPHover`. Write down the estimated regression equation, and interpret the coefficient on `MPHover` $(\hat{\beta_1})$. Make a scatterplot with the regression line.^[Hint: The simple `geom_smooth(method="lm")` is sufficient, so long as you use the right variables on the plot!]

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

Creating new variables as necessary, run a **log-linear** model of `Amount` on `MPHover`. Write down the estimated regression equation, and interpret the coefficient on `MPHover` $(\hat{\beta_1})$. Make a scatterplot with the regression line.^[Hint: The simple `geom_smooth(method="lm")` is sufficient, so long as you use the right variables on the plot!]

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part C

Creating new variables as necessary, run a **log-log** model of `Amount` on `MPHover`. Write down the estimated regression equation, and interpret the coefficient on `MPHover` $(\hat{\beta_1})$. Make a scatterplot with the regression line.^[Hint: The simple `geom_smooth(method="lm")` is sufficient, so long as you use the right variables on the plot!]

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part D

Which of the three log models has the best fit?^[Hint: Check $R^2$]

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

## Question 7

Return to the quadratic model. Run a quadratic regression of `Amount` on `Age`, `Age`$^2$, `MPHover`, and all of the race dummy variables. Test the null hypothesis: *"the race of the driver has no effect on Amount"*

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

## Question 8
